---
title: "乳癌/糖尿病 預測模型"
output: github_document
---

#資料前處理

```{r setup, include=FALSE}
install.packages("mlbench")
library(mlbench)
data(PimaIndiansDiabetes)
str(PimaIndiansDiabetes) 
head(PimaIndiansDiabetes)
knitr::opts_chunk$set(echo = TRUE)
```

'data.frame':	768 obs. of  9 variables:
 $ pregnant: num  6 1 8 1 0 5 3 10 2 8 ...
 $ glucose : num  148 85 183 89 137 116 78 115 197 125 ...
 $ pressure: num  72 66 64 66 40 74 50 0 70 96 ...
 $ triceps : num  35 29 0 23 35 0 32 0 45 0 ...
 $ insulin : num  0 0 0 94 168 0 88 0 543 0 ...
 $ mass    : num  33.6 26.6 23.3 28.1 43.1 25.6 31 35.3 30.5 0 ...
 $ pedigree: num  0.627 0.351 0.672 0.167 2.288 ...
 $ age     : num  50 31 32 21 33 30 26 29 53 54 ...
 $ diabetes: Factor w/ 2 levels "neg","pos": 2 1 2 1 2 1 2 1 2 2 ...

pregnant glucose pressure triceps insulin mass pedigree age diabetes
1        6     148       72      35       0 33.6    0.627  50      pos
2        1      85       66      29       0 26.6    0.351  31      neg
3        8     183       64       0       0 23.3    0.672  32      pos
4        1      89       66      23      94 28.1    0.167  21      neg
5        0     137       40      35     168 43.1    2.288  33      pos
6        5     116       74       0       0 25.6    0.201  30      neg

```{r cars}
PimaIndiansDiabetesC<-PimaIndiansDiabetes[complete.cases(PimaIndiansDiabetes),]
c(nrow(PimaIndiansDiabetes),nrow(PimaIndiansDiabetesC))
```

[1] 768 768

```{r cars}
PimaIndiansDiabetesC$Test<-F
PimaIndiansDiabetesC[
sample(1:nrow(PimaIndiansDiabetesC),nrow(PimaIndiansDiabetesC)/3),
]$Test<-T
c(sum(PimaIndiansDiabetesC$Test==F),sum(PimaIndiansDiabetesC$Test==T))
PimaIndiansDiabetesC$diabetes<-factor(PimaIndiansDiabetesC$diabetes,levels=c("pos","neg"))
```

[1] 512 256


#預測模型建立

```{r cars}
install.packages("caret")
install.packages("lattice")
install.packages("ggplot2")
summary(cars)
```

使用迴歸分析,糖尿病是否會得 將diabetes設為y,其他各變項當作x

```{r cars}
fit<-glm(diabetes~.,PimaIndiansDiabetesC[PimaIndiansDiabetesC$Test==F,],family="binomial")
library(MASS)
finalFit<-stepAIC(fit,direction = "both",trace = F)
summary(finalFit)$coefficients
```

                Estimate   Std. Error   z value     Pr(>|z|)
(Intercept)  9.466264125 0.8925268137 10.606140 2.790407e-26
pregnant    -0.093304393 0.0380076503 -2.454885 1.409298e-02
glucose     -0.036743580 0.0045629026 -8.052677 8.100264e-16
insulin      0.001672436 0.0009692421  1.725509 8.443574e-02
mass        -0.083795265 0.0171792018 -4.877716 1.073214e-06
pedigree    -0.895077294 0.3615793967 -2.475465 1.330626e-02
age         -0.026822173 0.0116341821 -2.305463 2.114067e-02


#預測模型驗證，解釋

```{r cars}
pimPred<-predict(finalFit,newdata = PimaIndiansDiabetesC[PimaIndiansDiabetesC$Test==T,])
pimAns<-ifelse(pimPred<0.5,"pos","neg") 
pimAns<-factor(pimAns,levels = c("pos","neg"))
#install.packages("caret")
#install.packages("lattice")
#install.packages("ggplot2")
library(caret)
sensitivity(pimAns,PimaIndiansDiabetesC[PimaIndiansDiabetesC$Test==T,]$diabetes)
specificity(pimAns,PimaIndiansDiabetesC[PimaIndiansDiabetesC$Test==T,]$diabetes)
posPredValue(pimAns,PimaIndiansDiabetesC[PimaIndiansDiabetesC$Test==T,]$diabetes)
negPredValue(pimAns,PimaIndiansDiabetesC[PimaIndiansDiabetesC$Test==T,]$diabetes)
summary(cars)
```

將正面的pos改成第一,sesitvity預測值約為0.696

sensitivity(pimAns,PimaIndiansDiabetesC[PimaIndiansDiabetesC$Test==T,]$diabetes)
[1] 0.6966292
specificity(pimAns,PimaIndiansDiabetesC[PimaIndiansDiabetesC$Test==T,]$diabetes)
[1] 0.7964072
posPredValue(pimAns,PimaIndiansDiabetesC[PimaIndiansDiabetesC$Test==T,]$diabetes)
[1] 0.6458333
negPredValue(pimAns,PimaIndiansDiabetesC[PimaIndiansDiabetesC$Test==T,]$diabetes)
[1] 0.83125

## GitHub Documents

This is an R Markdown format used for publishing markdown documents to GitHub. When you click the **Knit** button all R code chunks are run and a markdown file (.md) suitable for publishing to GitHub is generated.

## Including Code

You can include R code in the document as follows:

```{r cars}
BreastCancerC<-BreastCancer[complete.cases(BreastCancer),!names(BreastCancer)%in%c("Id")]
c(nrow(BreastCancer),nrow(BreastCancerC))
summary(cars)
```

## Including Plots

You can also embed plots, for example:

```{r pressure, echo=FALSE}
plot(pressure)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
